|

### 2019-01-17 Paper 2019.Rmd
Fixing arrests -> convictions

Since the 1970s, the U.S. Supreme Court has maintained that nearly all limits on political spending violate the first amendment’s protection of free speech. In its 1976 _Buckley v. Valeo_ decision, the Court laid out only two admissible justifications for limiting campaign donations: To prevent corruption or the appearance of corruption. But do campaign finance limits actually prevent corruption or its appearance? As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions. Using state-level data from 1990-2012 on contribution limits, corruption arrests, and media mentions of corruption, this paper employs linear panel regression and first differences analyses to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption. These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption.[^SPSA]

@@

The passage of the McCain-Feingold in 2002 inspired a wave of challenges to campaign contributions and expenditures, driven mostly by conservative and religious political groups. In 2007, the Court examined the McCain-Feingold ban on airing issue advertisements close to election. Banning such ads, the Court argued, would have a chilling effect on free speech, and it struck down the ban (_FEC v. Wisconsin Right to Life_). Then, in 2010, the Court issued what has become one of its most well-known rulings: In _Citizens United v. FEC_ (2010), it struck down limits on independent expenditures by outside groups, including corporations and unions. One critical aspect of _Citizens United_ is the establishment of the principle that, according to Justice Anthony Kennedy, “independent expenditures do not lead to, or create the appearance of, quid pro quo corruption.” The Court’s emphasis on quid pro quo corruption as the only justification for contribution limits extended the following year, as it struck down an Arizona effort to level the political playing field with matching state campaign funds (_Arizona Free Enterprise Club v. Bennett_, 2011).

Since 2011, the network of conservative legal groups behind Citizens United has continued to take aim at contribution limits as an unnecessary restriction of political speech, with a focus on individual contribution limits. The 1971 Federal Election Campaign Act placed a limit on the amount an individual could give to one campaign, in addition to two-year limits on the total amount an individual could give to political campaigns. In _McCutcheon v. FEC_ (2014) James Bopp, one of the attorneys behind the Citizens United challenge, convinced the Court of the unconstitutionality of total individual limits. Another case, _Holmes v. FEC_ (2017), targeted the distribution of individual campaign contribution across primary and general elections. In yet another, _Lair v. Motl_ (2017), Bopp once again took aim at individual contribution limits, arguing that the state of Montana had not shown compelling evidence that campaign contribution limits decreased the risk of corruption.

@@

I build a model of political corruption using control variables previously demonstrated by Alt and Lassen to be correlated with corruption arrests, resulting in a data set covering 1990-2004, the period of overlap among the data sets listed above. These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization. Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, I can better identify the association of campaign finance laws with corruption levels. For each of these models, I test fixed state and year effects and random effects. The models are as follows:

@@

### Model II: First Differences Model
Even if the panel modeling above fails to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption. In addition to the panel model above, I ran a first differences regression compare the state-years in which campaign finance laws changed to state-years where they remained constant. If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should be associated with lower CCI (corruption convictions) and CRI (reflections) in the years following.

@@

### Modeling campaign limits and corruption arrests 
The results of the panel regressions reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.

@@

### Modeling changes in campaign limits and corruption arrests

The final set of models (Table X) displays results from multiple first difference models designed to isolate the effect of changes in campaign finance laws on corruption arrests. None of the models find correlation between campaign finance limits and either corruption convictions or corruption reflections.

>>>>

Since the 1970s, the U.S. Supreme Court has maintained that nearly all limits on political spending violate the first amendment’s protection of free speech. In its 1976 _Buckley v. Valeo_ decision, the Court laid out only two admissible justifications for limiting campaign donations: To prevent corruption or the appearance of corruption. But do campaign finance limits actually prevent corruption or its appearance? As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions. Using state-level data from 1990-2012 on contribution limits, corruption convictions, and media mentions of corruption, this paper employs linear panel regression and first differences analyses to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption. These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption.[^SPSA]

@@

The passage of the McCain-Feingold in 2002 inspired a wave of challenges to campaign contributions and expenditures, driven mostly by conservative and religious political groups. In 2007, the Court examined the McCain-Feingold ban on airing issue advertisements close to election. Banning such ads, the Court argued, would have a chilling effect on free speech, and it struck down the ban ( _FEC v. Wisconsin Right to Life_). Then, in 2010, the Court issued what has become one of its most well-known rulings: In _Citizens United v. FEC_ (2010), it struck down limits on independent expenditures by outside groups, including corporations and unions. One critical aspect of _Citizens United_ is the establishment of the principle that, according to Justice Anthony Kennedy, “independent expenditures do not lead to, or create the appearance of, quid pro quo corruption.” The Court’s emphasis on quid pro quo corruption as the only justification for contribution limits extended the following year, as it struck down an Arizona effort to level the political playing field with matching state campaign funds (_Arizona Free Enterprise Club v. Bennett_, 2011).

Since 2011, the network of conservative legal groups behind Citizens United has continued to take aim at contribution limits as an unnecessary restriction of political speech, with a focus on individual contribution limits. The 1971 Federal Election Campaign Act placed a limit on the amount an individual could give to one campaign, in addition to two-year limits on the total amount an individual could give to political campaigns. In _McCutcheon v. FEC_ (2014) James Bopp, one of the attorneys behind the Citizens United challenge, convinced the Court of the unconstitutionality of total individual limits. Another case, _Holmes v. FEC_ (2017), targeted the distribution of individual campaign contribution across primary and general elections. In yet another, _Lair v. Mangan_ (2018), Bopp once again took aim at individual contribution limits, arguing that the state of Montana had not shown compelling evidence that campaign contribution limits decreased the risk of corruption.

@@

I build a model of political corruption using control variables previously demonstrated by Alt and Lassen to be correlated with corruption convictions, resulting in a data set covering 1990-2004, the period of overlap among the data sets listed above. These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization. Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, I can better identify the association of campaign finance laws with corruption levels. For each of these models, I test fixed state and year effects and random effects. The models are as follows:

@@

### Model II: First Differences Model
Even if the panel modeling above fails to capture correlation between state level campaign finance laws and corruption convictions, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption. In addition to the panel model above, I ran a first differences regression compare the state-years in which campaign finance laws changed to state-years where they remained constant. If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should be associated with lower CCI (corruption convictions) and CRI (reflections) in the years following.

@@

### Modeling campaign limits and corruption convictions 
The results of the panel regressions reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.

@@

### Modeling changes in campaign limits and corruption convictions

The final set of models (Table X) displays results from multiple first difference models designed to isolate the effect of changes in campaign finance laws on corruption convictions. None of the models find correlation between campaign finance limits and corruption convictions or corruption reflections.
